SIPESCA-B: a set of real data time series benchmark for traffic prediction

### 2015-06-12 paper.tex
un test
Revising abstract
Refs  #2 but could also ref #3. Mainly for revision by @pacastillo.

%En el ámbito de la gestión del tráfico no existen benchmarks públicos obtenidos a partir de datos reales disponibles para la comunidad, de forma que puedan probar sus métodos de extracción de información y comparar sus resultados con los obtenidos por otros investigadores. 
In the traffic management field no public real-data benchmarks are available to the research community, so that they can test their information extracting methods and compare their results with those obtained by other researchers.
%En este trabajo se presenta el benchmark SIPESCA-B, un conjunto de series temporales obtenidas a partir de la monitorización del tráfico en varios puntos de la red de carreteras andaluza. Se trata de datos reales relativos al número de vehículos que han pasado por ciertos puntos a lo largo de varios meses. Las series de datos se facilitan en formatos sencillos y ampliamente extendidos y se han dejado disponibles en un repositorio público.
In this work the benchmark SIPESCA-B, a set of time series obtained monitoring the traffic at several locations in the Andalusian road network, is presented. 
Time series are build using real data from the number of vehicles that have passed through certain locations along several months.
The datasets are provided in simple and widespread formats and are left available in a public repository.
%El objetivo de este trabajo es ofrecer acceso y detalles del benchmark propuesto a otros investigadores, así como unos resultados preliminares con varios métodos de predicción que sirvan para la comparación de futuros resultados publicados en el área de la gestión y predicción del tráfico.
Our aim with is providing public access and details of this benchmark as well as preliminary results with various prediction methods to the research community to serve as comparison of future results in the management and traffic prediction field.

@@

%Es por esto que muchos investigadores presentan sus trabajos usando simuladores de tráfico \cite{Morzy2007} o benchmarks artificiales para obtener datos con los que trabajar (aplicarles algoritmos de extracción de información o predicción). 
That is why many researchers present their work using traffic simulators \cite{Morzy2007} or artificial benchmarks to obtain data to which applying data mining or prediction algorithms.
%
% Linear Road Benchmark simulates a variable tolling system [6]
% The system uses the MIT Trac Simulator to generate moving vehicles
%
% The DynaMark Benchmark simulates the movement of mobile users  who update their location with an average periodicity. [14]
%
% COST Benchmark  simulated objects with periodically updated 2-D locations.   [12]
%
% The BerlinMOD benchmark, like LRB, simulates spatio-temporal data of moving vehicles on a road network [9]. 
%
% HE GSMARK BENCHMARK: The resulting data consists of a real road network with simulated moving vehicles \cite{Shen2011}
%
% \cite{Gidofalvi2010}
% data set contains the GPS readings of 1500 taxis and 400 trucks travelling on the streets of Stockholm
%
%Entre estos benchmarks sintéticos cabe destacar:
Among these synthetic benchmarks we can mention:
\begin{itemize}
  \item  \emph{Linear Road Benchmark} uses the \emph{MIT Trac Simulator} to simulate the movement of vehicles on a toll \cite{Arasu2004}.
  \item  \emph{DynaMark Benchmark} simulates the movement of users, updating its position with a certain frequency \cite{Myllymaki2003}.
  \item  \emph{COST Benchmark} simulates moving objects and periodically updates its 2D position \cite{Jensen2006}.
  \item  \emph{BerlinMOD Benchmark} simulates spatio-temporal data from vehicle movements on a real road network \cite{Duntgen2009}.
  \item  \emph{GSMARK Benchmark} generates data from a real road on which simulating the vehicle movements \cite{Shen2011}.
  \item  \emph{Transport and Logistics Division of the Department of Urban Planning and Environment} public benchmark, consisting of real data from the GPS position of 1500 taxis and 400 trucks moving through the streets of Stockholm \cite{Gidofalvi2010}.
\end{itemize}

>>>>

%En el ámbito de la gestión del tráfico no existen benchmarks públicos obtenidos a partir de datos reales disponibles para la comunidad, de forma que puedan probar sus métodos de extracción de información y comparar sus resultados con los obtenidos por otros investigadores. 
In the field of traffic management % management? Prediction? Traffic
                                % what? Rate? modelling? 
no public real-data benchmarks are available to the research
community % that we know of, siempre
for testing their information processing methods and compare their
results with those obtained by other researchers. % This implies
                                % that... or this is bad because... - JJ
%En este trabajo se presenta el benchmark SIPESCA-B, un conjunto de series temporales obtenidas a partir de la monitorización del tráfico en varios puntos de la red de carreteras andaluza. Se trata de datos reales relativos al número de vehículos que han pasado por ciertos puntos a lo largo de varios meses. Las series de datos se facilitan en formatos sencillos y ampliamente extendidos y se han dejado disponibles en un repositorio público.
In this work the benchmark SIPESCA-B, a set of time series obtained monitoring the traffic at several locations in the Andalusian road network, is presented. 
Time series are built using real data from the number of vehicles that
have passed through certain locations along several months. % not
                                % _all_ vehicles - JJ
The datasets are provided in simple formats with widespread use and
are left available in a public repository. 
%El objetivo de este trabajo es ofrecer acceso y detalles del
%benchmark propuesto a otros investigadores, así como unos resultados
%preliminares con varios métodos de predicción que sirvan para la
%comparación de futuros resultados publicados en el área de la gestión
%y predicción del tráfico. 
Our aim for this work is to provide public access and details of this benchmark
as well as preliminary results with various prediction methods to the
research community to serve as comparison of future results in the
field of
management and traffic prediction.

@@

%Es por esto que muchos investigadores presentan sus trabajos usando simuladores de tráfico \cite{Morzy2007} o benchmarks artificiales para obtener datos con los que trabajar (aplicarles algoritmos de extracción de información o predicción). 
That is why many researchers present their work using traffic
simulators \cite{Morzy2007} or artificial benchmarks to obtain data to
which applying data mining or prediction algorithms. % The existence
                                % of benchmarks contradicts what you
                                % said above - JJ
%
% Linear Road Benchmark simulates a variable tolling system [6]
% The system uses the MIT Trac Simulator to generate moving vehicles
%
% The DynaMark Benchmark simulates the movement of mobile users  who update their location with an average periodicity. [14]
%
% COST Benchmark  simulated objects with periodically updated 2-D locations.   [12]
%
% The BerlinMOD benchmark, like LRB, simulates spatio-temporal data of moving vehicles on a road network [9]. 
%
% HE GSMARK BENCHMARK: The resulting data consists of a real road network with simulated moving vehicles \cite{Shen2011}
%
% \cite{Gidofalvi2010}
% data set contains the GPS readings of 1500 taxis and 400 trucks travelling on the streets of Stockholm
%
%Entre estos benchmarks sintéticos cabe destacar:
Among these synthetic benchmarks we can mention:
\begin{itemize}
  \item  \emph{Linear Road Benchmark} uses the \emph{MIT Trac Simulator} to simulate the movement of vehicles on a toll \cite{Arasu2004}.
  \item  \emph{DynaMark Benchmark} simulates the movement of users, updating its position with a certain frequency \cite{Myllymaki2003}.
  \item  \emph{COST Benchmark} simulates moving objects and periodically updates its 2D position \cite{Jensen2006}.
  \item  \emph{BerlinMOD Benchmark} simulates spatio-temporal data from vehicle movements on a real road network \cite{Duntgen2009}.
  \item  \emph{GSMARK Benchmark} generates data from a real road on which simulating the vehicle movements \cite{Shen2011}.
  \item  \emph{Transport and Logistics Division of the Department of Urban Planning and Environment} public benchmark, consisting of real data from the GPS position of 1500 taxis and 400 trucks moving through the streets of Stockholm \cite{Gidofalvi2010}.
\end{itemize}
